---
title: "readme"
author: "Wagner Pinheiro"
date: "20 de junho de 2015"
output: html_document
---
# Exploratory Data Analysis - Course Project 2


```{r, message=FALSE}
# load data
source('loadLib.R')
readData()
```

----------------


## Question 1

> Q: Have total emissions from PM2.5 decreased in the United States from 1999 to 2008? 
> Using the base plotting system, make a plot showing the total PM2.5 emission 
> from all sources for each of the years 1999, 2002, 2005, and 2008.

```{r, message=FALSE}
makePlot1()
```

A: Yes, total emissions decreased

-----------

## Question 2

> Q: Have total emissions from PM2.5 decreased in the Baltimore City, Maryland
> (fips == 24510) from 1999 to 2008? Use the base plotting system to make a plot
> answering this question.

```{r, message=FALSE}
makePlot2()
```

A: Yes, emissions from PM2.5 decreased in the Baltimore City, Maryland.

---------


## Question 3

> Q: Of the four types of sources indicated by the type (point, nonpoint, onroad,
> nonroad) variable, which of these four sources have seen decreases in
> emissions from 1999–2008 for Baltimore City? Which have seen increases in
> emissions from 1999–2008? Use the ggplot2 plotting system to make a plot
> answer this question.

```{r, message=FALSE}
makePlot3()
```

A: 'Nonpoint', 'onroad', 'nonroad' type's decreases in emissions from 1999-2008. 
Only 'point' type emissions have increased in the same period

---------


## Question 4

> Q: Across the United States, how have emissions from coal combustion-related sources changed from 1999–2008?

```{r, message=FALSE}
makePlot4()
```

A: Emissions from coal combustion drecreased at low rates over time.

---------


## Question 5

> Q: How have emissions from motor vehicle sources changed from 1999–2008 in Baltimore City?

```{r, message=FALSE}
makePlot5()
```

A: Emissions declined at high rates between 1999-2002, and it is in continuous decline.

---------


## Question 6

> Q: Compare emissions from motor vehicle sources in Baltimore City with emissions from motor vehicle sources in Los Angeles County, California (fips == 06037). Which city has seen greater changes over time in motor vehicle emissions?

```{r, message=FALSE}
makePlot6()
```

A: There is a long road to L.A. decreased emissions.


---------

